### 2015-04-08 contract-language.tex
Added lattice for session guarantees.

\begin{figure}
\begin{smathpar}
\renewcommand{\arraystretch}{1.2}
\begin{array}{rclcl}
\multicolumn{5}{c}{
  {x,y,\cureff} \in \mathtt{EffVar} \qquad \qquad
  {\sf Op} \in \mathtt{OperName}
}\\
\cv 		& \in & \mathtt{Contract} 	& \coloneqq & \forall (x : \tau).\cv
        \ALT \forall x.\cv \ALT \pi \\
\tau		& \in	& \mathtt{EffType}	& \coloneqq &  {\sf Op}
        \ALT \tau \vee \tau \\
\pi			&	\in & \mathtt{Prop} & \coloneqq & \true \ALT R(x,y)
        \ALT \pi \vee \pi \\
			  & 		&	 &  \ALT & \pi \wedge \pi \ALT \pi \Rightarrow \pi \\
R				& \in & \mathtt{Relation}	& \coloneqq & \visZ \ALT \soZ
        \ALT \sameobjZ \ALT R^+ \\
				&			&	 &  \ALT & R \cup R \ALT R \cap R \\
\end{array}
\end{smathpar}
\caption{Contract language.}
\label{fig:contract-lang}
\end{figure}

@@

Here, the consistency level for an operation in this scheme is any combination
of the above guarantees. It is easy to see that there are 24 (4!) combinations,
which form a partially ordered consistency lattice with a height of 4.
Classifying a contract under this scheme amounts to determining the weakest
combination under which the contract will hold, and entails 24 comparisons at
worst. Under this scheme, \rcf{deposit} operations does not need any guarantees,
\rcf{getBalance} needs RYW and WFR ($\Delta \vdash \R{RYW} \wedge \R{WFR}
\Rightarrow \cv_{gb}$), and \rcf{withdraw} cannot be satisfied ($\Delta \vdash
\R{RYW} \wedge \R{MW} \wedge \R{MR} \wedge \R{WFR} \not\Rightarrow \cv_{w}$).

>>>>

\begin{figure}
\begin{smathpar}
\renewcommand{\arraystretch}{1.2}
\begin{array}{rclcl}
\multicolumn{5}{c}{
  {x,y,\cureff} \in \mathtt{EffVar} \qquad \qquad
  {\sf Op} \in \mathtt{OperName}
}\\
\cv 		& \in & \mathtt{Contract} 	& \coloneqq & \forall (x : \tau).\cv
        \ALT \forall x.\cv \ALT \pi \\
\tau		& \in	& \mathtt{EffType}	& \coloneqq &  {\sf Op}
        \ALT \tau \vee \tau \\
\pi			&	\in & \mathtt{Prop} & \coloneqq & \true \ALT R(x,y)
        \ALT \pi \vee \pi \\
			  & 		&	 &  \ALT & \pi \wedge \pi \ALT \pi \Rightarrow \pi \\
R				& \in & \mathtt{Relation}	& \coloneqq & \visZ \ALT \soZ
        \ALT \sameobjZ \ALT = \\
				&			&	 &  \ALT & R \cup R \ALT R \cap R \ALT R^+ \\
\end{array}
\end{smathpar}
\caption{Contract language.}
\label{fig:contract-lang}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[width=\columnwidth]{Figures/lattice}
\end{center}
\caption{Lattice of consistency levels under session guarantees.}
\label{fig:lattice}
\end{figure}

In this scheme, the consistency level of an operation is any combination of the
above guarantees, which form a partially ordered consistency lattice show in
Figure~\ref{fig:lattice}. Each element in this lattice corresponds to a
store-consistency level, and is represented by its contract. An edge from a
lower level element to an upper level element corresponds to logical
implication between their corresponding contracts. Classifying a contract under
this scheme is a directed search in the lattice, starting from the bottom, and
determining the weakest consistency level under which the contract can be
satisfied. Under this scheme, \rcf{deposit} operations does not need any
guarantees, \rcf{getBalance} needs RYW and WFR ($\Delta \vdash \R{RYW} \wedge
\R{WFR} \Rightarrow \cv_{gb}$), and \rcf{withdraw} cannot be satisfied ($\Delta
\vdash \R{RYW} \wedge \R{MW} \wedge \R{MR} \wedge \R{WFR} \not\Rightarrow
\cv_{w}$).
